---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# summaryStats

This package contains a function called "summaryStats" that can be used to create a dataframe that contains summary statistics for a given dataset.  The summary statistics that are calculated with this function include the mean, median, max, min, and sdev (standard deviation). 

The function has two mandatory arguments. The first argument (dataset_of_interest) requires the user to input a dataframe. The second argument (col_of_interest) requires the user to input a numeric column in the dataset, that the user wishes to calculate summary statistics on.

The function also has an optional third argument, which is FALSE by default. If the user inputs TRUE, then this function will also export a csv file called "results.csv" which contains the results of the calculated summary statistics.

## Installation

This package is not published on CRAN, so in order to use it, you need to download it from this repository. You can install summaryStats from [GitHub](https://github.com/) using the following line of code:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2021/lorenzolindoPackage")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(summaryStats)
library(datateachr)
summaryStats(vancouver_trees, height_range_id)
```
